Checkpoint 3

### 2020-04-23 Checkpoint3.Rmd
Update Checkpoint3.Rmd

@@

### Demographic 
```{r}
#Demographic: Identification 
Finaldata <- data.frame(Finaldata) %>% mutate(state = State)
plot_usmap(data = Finaldata, values = "percent_white", color = "white") + 
  scale_fill_continuous(name = "Percent White", label = scales::comma) + 
  theme(legend.position = "right")+ ggtitle("Percent of Residents that Identify as White") + 
  theme(
plot.title = element_text(color="Black", size=14, face="bold")
)

@@

#By Results 
plot_usmap(data = Finaldata, values = "percent_asian", color = "white") + 
  scale_fill_continuous(low = "sky blue", high = "black", name = "Percent Asian", label = scales::comma) + 
  theme(legend.position = "right") + ggtitle("Percent Asian by General Election Results")+
  theme(
plot.title = element_text(color="Black", size=14, face="bold")
) + facet_wrap(~Winner)

#By income 
plot_usmap(data = Finaldata, values = "per_capita_income", color = "white") + 
  scale_fill_continuous(low = "sky blue", high = "black", name = "$ Per Capita", label = scales::comma) + 
  theme(legend.position = "right") + ggtitle("Percent Capita Income")+
  theme(
plot.title = element_text(color="Black", size=14, face="bold")
)

#Income by state affiliation 
ggplot(Finaldata, aes(x = per_capita_income, fill = StateColor)) + 
    geom_density(alpha = .8)+ ggtitle("Income per Capita") + xlab("$") + ylab("Density")

#Trump Support 
ggplot(Finaldata, aes(x = percent_republican2016)) + 
    geom_density()+ ggtitle("Trump Support During the 2016 Elections") + xlab("Percent of Trump Support") + ylab("Density")

@@

ggplot(Finaldata, aes(x = per_capita_income)) + 
    geom_density()+ ggtitle("Per Capita Income") + xlab("Per Capita Income") + ylab("Density") + facet_wrap(~Winner)
```

@@

```{r}
## Creating a df of just the cases the week before 3/17
weekbefore <- data.frame(Finaldata) %>% filter(Day <= as.character(as.Date("2020-03-17")))

@@

```
```{r}
ggplot(Finaldata, aes(x = Day, y = ChinaVirusInterest, color = factor(State))) + 
    geom_point() + 
    geom_smooth(method = "lm", se = FALSE) + 
    facet_wrap(~ State) + 
    theme(legend.position = "none")
```
\
\

>>>>

#Functions

@@

### Demographic 
```{r}
#Demographic: Identification 
Finaldata <- data.frame(Finaldata) %>% mutate(state = State)

@@

#Income by state affiliation 
ggplot(Finaldata, aes(x = per_capita_income, fill = StateColor)) + 
    geom_density(alpha = .8)+ ggtitle("Income per Capita") + xlab("$") + ylab("Density") +scale_fill_manual(values=c("blue", "purple", "red"))

#Trump Support

plot_usmap(data = Finaldata, values = "percent_republican2016", color = "white") + 
  scale_fill_continuous(low = "sky blue", high = "black", name = "Trump Support", label = scales::comma) + 
  theme(legend.position = "right") + ggtitle("Percent of Residents that Identify as Asian") +
  theme(plot.title = element_text(color="Black", size=14, face="bold"))

@@

@@

```{r echo=FALSE}
## Creating a df of just the cases the week before 3/17
#Scale.fill color manual ??? so to go from green to red
weekbefore <- data.frame(Finaldata) %>% filter(Day <= as.character(as.Date("2020-03-17")))

@@

```{r}
ggplot(Finaldata, aes(x = Day, y = ChinaVirusInterest, color = factor(State))) + 
    geom_point() + 
    geom_smooth(method = "lm", se = FALSE) + 
    facet_wrap(~ Region) + 
    theme(legend.position = "none")
```
\
\
